### 2023-05-11 acronyms/acronyms.tex
reset

%%%%%%put this in preamble
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries
%%%%%

%%%%% put this in right before draft
%%%%% acronyms
% alphabetical ordering is automated
\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
\newacronym{anl}{ANL}{Argonne National Laboratory}
\newacronym{inl}{INL}{Idaho National Laboratory}
\newacronym{npp}{NPP}{Nuclear Power Plant}
\newacronym{nrs}{NHRES}{Nuclear Renewable Hybrid Energy System}
\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
\newacronym{smr}{SMR}{Small Modular Reactor}
\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
\newacronym{nus}{NuScale}{NuScale Power, LLC}
\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
\newacronym{epri}{EPRI}{Electric Power Research Institute}
\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
\newacronym{ci}{CI}{Consistency Index}
\newacronym{cr}{CR}{Consistency Ratio}
\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
\newacronym{lwr}{LWR}{Light Water Reactor}
\newacronym{aps}{APS}{Arizona Public Service} 
\newacronym{arm}{ARMA}{Autoregressive Moving Average} 
\newacronym{eia}{EIA}{Energy Information Agency}
\newacronym{epa}{EPA}{Environmental Protection Agency}
\newacronym{hx}{HX}{Heat exchanger} 
\newacronym{msf}{MSF}{Multi-Stage Flash Distillation} 
\newacronym{mwe}{MWe}{Megawatts electricity}
\newacronym{mwt}{MWth}{Megawatts thermal energy}
\newacronym{ies}{IES}{Integrated Energy System} 
\newacronym{pv}{PV}{Palo Verde Generating Station} 
\newacronym{rav}{RAVEN}{Risk Analysis Virtual Environment} 
\newacronym{ro}{RO}{Reverse Osmosis} 
\newacronym{rom}{ROM}{Reduced Order Model} 
\newacronym{spe}{SPECO}{Specific Exergy Costing} 
\newacronym{ufs}{U-FSAR}{Updated Final Safety Analysis Report} 
\newacronym{ieo}{IESO}{Independent Electricity System Operator}
\newacronym{us}{US}{United States}
\newacronym{med}{MED}{Multiple-Effect Distillation}
\newacronym{ed}{ED/EDR}{Electrodialysis Reversal}
\newacronym{nf}{NF}{Nanofiltration}
\newacronym{jls}{J}{Joules}
\newacronym{nre}{NREI}{Nuclear Renewable Energy Integration}
\newacronym{nrt}{NRTL}{Aspen Electrolyte Non-Random Two-Liquid}
\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
\newacronym{ide}{IDE}{Israel Desalination Enterprises} 
\newacronym{iso}{ISO}{Independent System Operator} 
\newacronym{msf}{MSF}{Multi-Stage Flash} 
\newacronym{npt}{NPT}{Treaty on the Non-Proliferation of Nuclear Weapons}
\newacronym{un}{UN}{United Nations}
\newacronym{ict}{ICT}{Information and communications technologies}
\newacronym{nws}{NWS}{Nuclear Weapons States}
\newacronym{nnws}{NNWS}{Non Nuclear Weapons States}
\newacronym{iaea}{IAEA}{International Atomic Energy Agency}
\newacronym{snm}{SNM}{Special Nuclear Material}
\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
\newacronym{nnsa}{NNSA}{National Nuclear Security Administration}
\newacronym{fbi}{FBI}{Federal Bureau of Investigation}
\newacronym{nsg}{NSG}{Nuclear Suppliers Group}
\newacronym{mad}{MAD}{Mutually Assured Destruction}
\newacronym{wmd}{WMD}{Weapons of Mass Destruction}
\newacronym{sq}{SQ}{Significant Quantity}
\newacronym{der}{DER}{Distributed Energy Resource}
\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
\newacronym{usa}{US}{United States}
\newacronym{doe}{DOE}{United States Department of Energy}
\newacronym{pfc}{PFC}{Primary Frequency Control}
\newacronym{sfc}{SFC}{Secondary Frequency Control}
\newacronym{ace}{ACE}{Area Control Error}
\newacronym{var}{VAr}{Volt-Amps Reactive}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{nyi}{NYISO}{New York Independent System Operator}
\newacronym{ac}{AC}{Alternating Current}
\newacronym{dc}{DC}{Direct Current}
\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
\newacronym{inc}{I\&C}{Instrumentation and Controls}
%%%%%

%%%%%put this in the document where the acronym list will appear - Acronyms is in section format
\printnoidxglossary%[title{}] %removes automated Acronyms title too add custom
%%%%%

>>>>

%put this in preamble
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries
%%%%% acronyms
% alphabetical ordering is automated
\newacronym{anl}{ANL}{Argonne National Laboratory}
\newacronym{aps}{APS}{Arizona Public Service} 
\newacronym{arm}{ARMA}{Autoregressive Moving Average} 
\newacronym{eia}{EIA}{Energy Information Agency}
\newacronym{epa}{EPA}{Environmental Protection Agency}
\newacronym{epri}{EPRI}{Electric Power Research Institute}  
\newacronym{hx}{HX}{Heat exchanger} 
\newacronym{ide}{IDE}{Israel Desalination Enterprises} 
\newacronym{inl}{INL}{Idaho National Laboratory} 
\newacronym{iso}{ISO}{Independent System Operator} 
\newacronym{msf}{MSF}{Multi-Stage Flash} 
\newacronym{mwe}{MWe}{Megawatts electricity}
\newacronym{mwt}{MWth}{Megawatts thermal energy}
\newacronym{nerc}{NERC}{North American Electric Reliability Corporation} 
\newacronym{npp}{NPP}{Nuclear Power Plant} 
\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission} 
\newacronym{ies}{IES}{Integrated Energy System} 
\newacronym{ornl}{ORNL}{Oak Ridge National Laboratory} 
\newacronym{pv}{PV}{Palo Verde Generating Station} 
\newacronym{rav}{RAVEN}{Risk Analysis Virtual Environment} 
\newacronym{ro}{RO}{Reverse Osmosis} 
\newacronym{rom}{ROM}{Reduced Order Models} 
\newacronym{smr}{SMR}{Small Modular Reactor} 
\newacronym{spe}{SPECO}{Specific Exergy Costing} 
\newacronym{ufs}{U-FSAR}{Updated Final Safety Analysis Report} 
\newacronym{ahp}{AHP}{Analytic Hierarchy Procedure}
\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
\newacronym{ies}{IESO}{Independent Electricity System Operator}
\newacronym{npt}{NPT}{Treaty on the Non-Proliferation of Nuclear Weapons}
\newacronym{un}{UN}{United Nations}
\newacronym{ict}{ICT}{Information and communications technologies}
\newacronym{nws}{NWS}{Nuclear Weapons States}
\newacronym{nnws}{NNWS}{Non Nuclear Weapons States}
\newacronym{iaea}{IAEA}{International Atomic Energy Agency}
\newacronym{snm}{SNM}{Special Nuclear Material}
\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
\newacronym{nnsa}{NNSA}{National Nuclear Security Administration}
\newacronym{fbi}{FBI}{Federal Bureau of Investigation}
\newacronym{nsg}{NSG}{Nuclear Suppliers Group}
\newacronym{mad}{MAD}{Mutually Assured Destruction}
\newacronym{wmd}{WMD}{Weapons of Mass Destruction}
\newacronym{sq}{SQ}{Significant Quantity}
\newacronym{iaea}{IAEA}{International Atomic Energy Agency}
\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
\newacronym{der}{DER}{Distributed Energy Resource}
\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
\newacronym{usa}{US}{United States}
\newacronym{doe}{DOE}{United States Department of Energy}
\newacronym{pfc}{PFC}{Primary Frequency Control}
\newacronym{sfc}{SFC}{Secondary Frequency Control}
\newacronym{ace}{ACE}{Area Control Error}
\newacronym{var}{VAr}{Volt-Amps Reactive}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{nyi}{NYISO}{New York Independent System Operator}
\newacronym{epri}{EPRI}{Electric Power Research Institute}
\newacronym{ac}{AC}{Alternating Current}
\newacronym{dc}{DC}{Direct Current}
\newacronym{eia}{EIA}{United States Energy Information Administration}
\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
\newacronym{inc}{I\&C}{Instrumentation and Controls}
%\newacronym{}{}{}
%%%%%
%put this in the document somewhere
\printnoidxglossary
%%%%
